---
title: "Table 8. QUADAS'
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


```{r global_options8, include=F}
# see http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=F, warning=FALSE, message=FALSE, 
                      results='hide')

require(knitr)
library(reshape2)
library(ggplot2)
library(car)
library(plyr)
library(tables)
library(data.table)
library(htmlTable)

library(ztable)
options(ztable.type="html")
#read_chunk('make-data.R') # call program that forms data frame

```


```{r prep8}
# read in QUADAS data and provide a summary of all variables.

setwd("C:/Users/vonholle/Dropbox/unc.grad.school/misc/practicum/bpsr/backup")

dat.q.all = read.csv(file="quadas-2-2015-12-11.csv",
         head=T,
         sep=",")

dim(dat.q.all)
colnames(dat.q.all)
sapply(dat.q.all, class)

# take out excluded papers from full text review
# file from make-data.R file
include.ids = dat.ts$id

# ids are in 2nd column for the quadas .csv file above

dat.q = dat.q.all[dat.q.all$Paper.ID %in% include.ids,]
nrow(dat.q);nrow(dat.q.all)

```

<!--
NOTE: May need to exclude based on id from full text review data set.
-->

```{r prep8-2}
#summary(dat.q[,c(7:10,14:16,18:21,23:27)]) # note: have to avoid the free text fields. something about utf characters.

dat2 = dat.q[,c(7:10,14:16,18:21,23:27)] # short answer questions


# see http://stackoverflow.com/questions/31007915/print-a-frequency-table-of-a-factor-with-kable-in-rmarkdown
sapply(dat2, table)

# convert resposes from long to short response with only one letter:
# High = H
# Low = L
# Yes = Y
# No = N
# Unclear = U
# ..........................................

dat3 = as.data.frame(apply(dat2, 2, function(x) {
  x = ifelse(x=="Yes", "Y",
             ifelse(x=="No", "N",
                    ifelse(x=="Unclear", "U",
                           ifelse(x=="High", "H",
                                  ifelse(x=="Low", "L", NA)))))
}))

class(dat3) # check
table(dat3[,1]) # check
colnames(dat3) # check

# Use current variable names (you can evaluated in tables above) to make an abbreviated version for table
# ..........................................................

colnames(dat3) = c("Random", "Case-control", "Exclusion",
                   "Selection", "Knowledge-index", "Threshold",
                   "Concern-index", "Reference standard", "Knowledge-reference", 
                   "Bias-index", "Reference-match", "Interval",
                   "Reference-all", "Reference-same", "Include-all",
                   "Flow")

# 
# sapply(dat2, function(x) {kable(data.frame(t(as.matrix(table(x)))))})
# 
# dt = data.table(dat2)
# dt[, lapply(.SD, table, na.rm=TRUE) ] 
```


```{r, results='hide'}
dat.4 = cbind("Author, Year"=paste(dat.q$First.Author,
                                 dat.q$Publication.Year, 
                                 sep=", "),
            dat3)
dat.4 = dat.4[order(dat.4$'Author, Year'),]
rownames(dat.4)  = NULL

kable(dat.4)
```


```{r, results='asis'}

options(ztable.colnames.bold=TRUE)

zt = ztable(dat.4,
            zebra=2,
            zebra.color = "platinum", 
            caption="QUADAS 2 Quality Measures$^a$")

print(zt)
```
$^a$ For responses, Y=Yes, N=No, U=Unclear, H=High, L=Low.

For questions as defined in [QUADAS-2](http://annals.org.libproxy.lib.unc.edu/article.aspx?articleid=474994), 

**Random** = Was a consecutive or random sample of patients enrolled?,

**Case-control** = Was a case-control design avoided?,
Exclusion = Did the study avoid inappropriate exclusions?,

**Selection** = Could the selection of patients have introduced bias? (RISK),

**Knowledge-index** = "Were the index test results interpreted without knowledge of the results of the reference standard?",

**Threshold** = If a threshold was used, was it pre-specified?,

**Concern-index** = Is there concern that the index test, it's conduct or interpretation different from the review question (CONCERN)?,

**Reference standard** = Is the reference standard likely to classify the target condition?,

**Knowledge-reference** = Were the reference standard results interpreted without knowledge of the results of the index test?,

**Bias-index** = Could the conduct or interpretation of the index test have introduced bias (RISK)?,

**Reference-match** = Is there concern that the target condition as defined by the reference standard does not match the review question?,

**Interval** = Was there an appropriate interval between index tests and reference standard?,

**Reference-all** = Did all patients receive a reference standard?,

**Reference-same** = Did patients receive the same reference standard?,

**Include-all** = Were all patients included in the analysis?,
Flow = Could the patient flow have introduced bias (RISK)?
