---
title: "Tables 1-11"
author: ''
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r global_options, echo=FALSE, warning=FALSE, message=FALSE,results='hide'}
# see http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=F, warning=FALSE, message=FALSE, 
                      results='hide')

require(knitr)
library(reshape2)
library(ggplot2)
library(car)
library(plyr)
library(tables)
library(data.table)
library(htmlTable)
library(ztable)
library(compare)
options(ztable.type="html")
```

```{r}
read_chunk('make-data.R') # call program that forms data frame
```

# Introduction

The following tables are created from a series of R scripts, accessible at a [public github repository](https://github.com/avonholle/bpsr-2015). Data source is from data entered starting in 2015 at [http://bpsr.web.unc.edu/](http://bpsr.web.unc.edu/). The entire sequence of programs required to create this html document can be found in the [tables.Rmd](https://raw.githubusercontent.com/avonholle/bpsr-2015/main/tables.Rmd) document.

<!--
Note: all chunks have to have unique names, if there are names.
-->


```{r part1} 
# Read in data, dat.1, from the make-data.R program in options
# Also make a long form data frame, dat.ts.long, for tables 2, 4, 6 and 9
```

```{r child = 'var.vals.Rmd', eval=FALSE}
# create a data dictionary with abbreviated variable names.

```

---

# Table 1

```{r child = 'table1.Rmd'}
```

---

# Table 2

```{r child = 'table2.Rmd'}
```

---

# Table 3

```{r child = 'table3.Rmd'}
```

---

# Table 4

```{r child = 'table4.Rmd'}
```

---

# Table 5

```{r child = 'table5.Rmd'}
```

---

# Table 6

```{r child = 'table6.Rmd'}
```

---

# Table 7

```{r child = 'table7.Rmd'}
```


---

# Table 8, preliminary QUADAS descriptives.

This needs to be revised to match table 2 from [doi: 10.1136/bmj.d3621](http://dx.doi.org/10.1136/bmj.d3621)

```{r child = 'table8.Rmd'}
```


# Table 9

```{r child = 'table9.Rmd'}
```

---


```{r child = 'table10.Rmd', eval=F}
# Table 10, summary of exclusion status, including papers that did not have an exclusion field (entered before 10/13/2015)
# NOTE: need to go back and edit the labels. Excluded papers are correct, but the combos of before/after are not. maybe just get rid of this table?
```

---

# Table 11, table with reasons for exclusions

```{r child = 'table11.Rmd'}
```

